Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-08-18 doc/bcspaper/article.tex
made some changes in accordance with maria's suggestions

\subsection*{Paper Processing and classification}
%Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)

In order to obtain automatic labeling of sentences in a paper with CoreSC
concepts we first needed to convert the papers to a format that the the CoreSC
classifier, SAPIENTA can analyse.  Currently, SAPIENTA supports the SciXML and
PubMed Central DTDs.  Papers in PDF format are first converted to XML using
PDFX , a free service hosted by the University of Manchester
\cite{Constantin2013}. Once the paper has been split into sentences, SAPIENTA
is used to annotate each sentence with a relevant CoreSC label. These labels
are assigned using a conditional random fields model based upon a number of
features such as the sentence's location within the paper and pairs and
triplets of words found consecutively within the sentence \cite{Liakata2012}.
The SAPIENTA system has been trained on a corpus of 265 chemistry and
biochemistry papers and we have done no domain adaptation for the papers in
PLoS.

@@

We inspected the detail of a single decision tree, grown on the entire dataset,
to give further insight into which CoreSC class decisions were responsible for
the paper type predictions. This was a very large tree, with a depth of 37
nodes in places.  The first decision was based upon the number of Background
sentences in the article. Low Background percentages, of less than 0.694
indicates a Correspondence paper. 28 out of the 31 Correspondence papers were
correctly labelled by this decision  classified by this decision as
Correspondence were correctly labelled.

>>>>

\subsection*{Paper Processing and Classification}
%Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)

In order to obtain automatic labeling of sentences in a paper with CoreSC
concepts we first needed to convert the papers to a format that the the CoreSC
classifier, SAPIENTA can analyse.  Currently, SAPIENTA supports the SciXML and
PubMed Central DTDs.  Papers in PDF format are first converted to XML using
PDFX , a free service hosted by the University of Manchester
\cite{Constantin2013}. Once the paper has been split into sentences with
Liakata's SSplit tool \cite{liakata2009semantic}, SAPIENTA is used to annotate
each sentence with a relevant CoreSC label. These labels are assigned using a
conditional random fields model based upon a number of features such as the
sentence's location within the paper and pairs and triplets of words found
consecutively within the sentence \cite{Liakata2012}.  The SAPIENTA system has
been trained on a corpus of 265 chemistry and biochemistry papers and we have
done no domain adaptation for the papers in PLoS.

@@

We inspected the detail of a single decision tree, grown on the entire dataset,
to gain further insight into which CoreSC class decisions were responsible for
the paper type predictions. This was a very large tree, with a depth of 37
nodes in places.  The first decision was based upon the number of Background
sentences in the article. Low Background percentages, of less than 0.694
indicates a Correspondence paper. 28 out of the 31 Correspondence papers were
correctly classified by this decision.
